quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-22 paper-quollr.Rmd
Changed the buffer size defaults and add restriction that could only have values less than vector or horizontal spacing

```{r}
all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 x_start = NA, y_start = NA, 
                                                 buffer_x = NA, buffer_y = NA, 
                                                 hex_size = 0.2)

>>>>

```{r}
all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 x_start = NA, y_start = NA, 
                                                 hex_size = 0.2)

### 2024-02-22 paper-quollr.tex
Changed the buffer size defaults and add restriction that could only have values less than vector or horizontal spacing

\begin{verbatim}
all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 x_start = NA, y_start = NA, 
                                                 buffer_x = NA, buffer_y = NA, 
                                                 hex_size = 0.2)

>>>>

\begin{verbatim}
all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 x_start = NA, y_start = NA, 
                                                 hex_size = 0.2)
